ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-24 pyked.tex
edits through the end of section 3

Therefore, we believe there remains a need for an open, community-focused and
developed, combustion\slash chemical kinetics data format. In this work, we
present a new, open-source, human- and machine-readable data standard for
fundamental combustion experiments, \ck{}, and offer tools for easily working
with data encoded in this format. Niemeyer recently introduced an initial
version of the \ck{} format~\autocite{Niemeyer:2016wf}, and in this work we
further formalize and develop the standard. We also discuss a related Python
software tool for validating and working with \ck{} files: \pk{}. Our
motivations are similar those of the PrIMe and ReSpecTh teams: the \ck{} project
will enable easy sharing and use of fundamental combustion data, for the
(primary) purposes of developing and validating predictive chemical kinetic
models. However, we make usability a major design focus, and plan to share all
data and software openly to cultivate a community of user-contributors.

@@

This section will provide a brief introduction to the current version of the
\ck{} database format, v0.1.6, which represents a functional standard
for documenting autoignition measurements in shock tubes and rapid compression machines.
Here we do not include a complete listing of available fields; a complete reference for the
schema can be found in the online documentation.
\footnote{\url{https://pr-omethe-us.github.io/PyKED/schema-docs.html}}
In addition, in Section~\ref{sec:usage-example}, we will provide examples of \ck{}
files. We indicate \yabox|yaml| keywords or values using text with gray background,
and \pybox|Python| code using text with a yellow background.

\ck{} files use the YAML data serialization format~\autocite{yaml:1.2}. This
format offers the advantages of being human readable, written in plain text, and
having parsers in most common programming languages, including Python, C++, Java,
Perl, MATLAB, and many others. The YAML syntax is quite simple: the basic file
structure is made of mappings, delimited by a colon. The key for the mapping is
on the left of the colon, and the value on the right can be a single value,
a sequence of values, a nested mapping, or some combination of these:
%
\begin{yamlbox}
key1: value  # Single-value mapping
key2:  # Sequence format
  - value
  - value
key3:  # Nested mapping
  key4: 0
key5:  # Sequence of mappings
  - key-s1: 0
    key-s2: value
  - key-s2: value
    key-s1: 0
\end{yamlbox}

The \yabox|value| can be a string, integer, or floating point number. The \ck{}
format is designed to include all of the information necessary to simulate a
given experiment. A \ck{} file can generally be broken into two main sections.
The first section details all of the ``meta'' information about the experiment
and the \ck{} file. In this section, the common \yabox|author| mapping is used
for any fields where an author must be specified. The \yabox|author| mapping
contains the following fields:
%
\begin{itemize}
    \item \yabox|name| (required, string): The author's full name
    \item \yabox|ORCID| (optional, string): the author's ORCID number
\end{itemize}
%
More generally for the meta information, the required keys in this section
are:
%
\begin{itemize}
    \item \yabox|file-author| (required, \yabox|author|-type mapping): The
    author of the \ck{} file
    \item \yabox|file-version| (required, integer): The version of the \ck{}
    file
    \item \yabox|chemked-version| (required, string): The version of the \ck{}
    schema that this file conforms to
    \item \yabox|reference| (required, mapping): The reference information for
    the article associated with the data in the file. The fields in this
    mapping are:
    \begin{itemize}
        \item \yabox|authors| (required, sequence): A sequence of \yabox|author|
        mappings
        \item \yabox|journal| (required, string): The name of the publishing
        journal
        \item \yabox|year| (required, integer): The year of publication
        \item \yabox|doi| (optional, string): The article DOI
        \item \yabox|volume| (required, integer): The journal volume number
        \item \yabox|pages| (optional, string): The article pages
        \item \yabox|detail| (optional, string): A description of from where the
        data originated (e.g., figure or table number)
    \end{itemize}
    \item \yabox|experiment-type| (required, string): Currently, only
    \yabox|ignition delay| is supported
    \item \yabox|apparatus| (required, string): The type of apparatus used to
    perform the experiment (\yabox|shock tube| or \yabox|rapid compression machine|)
\end{itemize}

The second section of the file encodes the experimental data. In the \ck{} file,
this is done in a sequence of mappings, with the following information required
in each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units
    \item \yabox|pressure| (required, string): The pressure of the experiment,
    with units
    \item \yabox|composition| (required, sequence): The composition of the
    mixture in the experiment, a sequence of mappings with the following fields
    \begin{itemize}
        \item \yabox|species-name| (required, string): The name of the species
        \item \yabox|mole-fraction|, \yabox|mass-fraction|, \yabox|mole-percent|
        (required, float): The mole fraction or percent, or the mass fraction.
        Only one of the three is permitted in a given \yabox|composition|
        sequence.
        \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
        \yabox|elemental-composition| (required, string or sequence): The InChI
        or SMILES representing the molecule, or its atomic or elemental
        composition (\yabox|atomic-composition| and
        \yabox|elemental-composition| are synonyms) as a sequence
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The type of ignition
    measured in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How the ignition delay was
        measured; one of \yabox|d/dt max| to indicate the ignition point is
        found at the maximum of the time derivative of the \yabox|target|,
        \yabox|max| or \yabox|min| to indicate the ignition point is at the
        maximum or minimum of the \yabox|target|, or \yabox|1/2 max| to
        indicate the half-maximum point
        \item \yabox|target| (required, string): The target for the type of the
        ignition point; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

The top-level key for the sequence is called \yabox|datapoints|. Each of the
quantities in an element must be specified with units. This should be done as a
single string associated with the first element of the sequence. The units of
the quantity are validated to ensure they have the appropriate dimensionality
for the quantity. In addition, each of the quantities in an element can
optionally be assigned an uncertainty. This uncertainty can be either absolute
or relative, and is specified as elements of the sequence of the associated key.
For example, the absolute uncertainty of the temperature and the relative
uncertainty of the ignition delay might be specified as follows:

\begin{yamlbox}
datapoints:
  - temperature:
      - 1100 kelvin
      - uncertainty-type: absolute
        uncertainty: 10 kelvin
    ignition-delay:
      - 10 us
      - uncertainty-type: relative
        uncertainty: 0.1
    ...
\end{yamlbox}

\ck{} files are stored online in a git repository hosted on GitHub.
\footnote{\url{https://github.com/pr-omethe-us/ChemKED-database}}
Submissions from the community are welcomed and can be made via the standard Pull Request
on GitHub. The authors also encourage questions and problems to be submitted either via
email or as Issues on GitHub. In particular, researchers interested in converters for
internal data formats to the \ck{} format are encouraged to reach out. In addition,
the \pk{} package (described in more detail in Sec.~\ref{sec:pyked-architecture})
provides converters to and from the ReSpecTh format~\autocite{Varga2015b}.

%====================================================================
\section{PyKED architecture}\label{sec:pyked-architecture}
%
\pk{} is a Python package that currently provides the reference implementation
of the interface to \ck{} files~\autocite{PyKED}. \pk{} reads \ck{} files, validates
their structure and content, and allows the user to interact with the data contained
in the \ck{} file.

The basic user interface to the \ck{} file in \pk{} is through the
\pybox|ChemKED| class. The \pybox|ChemKED| class constructor takes the filename
of a \ck{} file or a Python dictionary containing the contents of a \ck{} file
as its argument. When the file or dictionary is loaded, it is validated to have
the correct format by the Python package Cerberus \autocite{cerberus}. The
schema used for validation of the \ck{} files is available publicly in the
\texttt{schemas} directory of the PyKED source code
repository.\footnote{\url{https://github.com/pr-omethe-us/PyKED/tree/master/pyked/schemas}}
To ease extension of the schema to describe other experimental measurements, it
comprises multiple YAML files.

@@

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class, information in the
\pybox|DataPoint| is stored as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only, no validation is done of the
    value.
    \item \pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|,
    \pybox|pressure_rise|: The value of these data are stored as instances of
    the \pybox|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole-percent|,
    \yabox|mole-fraction|, or \yabox|mass-fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole-percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole-percent'|,
    \pybox|'mole-fraction'|, or \pybox|'mass-fraction'|
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
    \item \pybox|compression_time|: If the \ck{} file encodes an RCM experiment,
    the length of the compression stroke may be included
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
\end{itemize}

The \pybox|DataPoint| class defines two instance methods:
\pybox|get_cantera_mole_fraction()| and \pybox|get_cantera_mass_fraction()|.
With these methods, the composition of the reactant mixture can be output to a
format that can be used to set the composition of a
Cantera~\pybox|Solution|~\autocite{Cantera:2.3.0}.
The \pybox|composition| specification does not contain the molecular
weights of the components, so conversion between mole fractions and mass
fractions is not currently possible.

The \pybox|ChemKED| class defines one instance method:
\pybox|get_dataframe()|. Using this method, the user can get an instance of a
Pandas \pybox|DataFrame|~\autocite{pandas} that contains the information in the
list of \pybox|DataPoint|s. The user can specify the columns included in the
\pybox|DataFrame| by passing a list of column names to the
\pybox|output_columns| argument of the \pybox|get_dataframe()| method. The
possible columns are not case-sensitive and are:

\noindent\begin{itemize*}
    \item \pybox|'Temperature'|
    \item \pybox|'Pressure'|
    \item \pybox|'Ignition Delay'|
    \item \pybox|'Composition'|
    \item \pybox|'Equivalence Ratio'|
    \item \pybox|'Reference'|
    \item \pybox|'Apparatus'|
    \item \pybox|'Experiment Type'|
    \item \pybox|'File Author'|
    \item \pybox|'File Version'|
    \item \pybox|'ChemKED Version'|
\end{itemize*}

In addition, specific fields from the \pybox|Reference| and \pybox|Apparatus|
attributes can be included by specifying the name after a colon. These options
are:

\noindent\begin{itemize*}
    \item \pybox|'Reference:Volume'|
    \item \pybox|'Reference:Journal'|
    \item \pybox|'Reference:DOI'|
    \item \pybox|'Reference:Authors'|
    \item \pybox|'Reference:Detail'|
    \item \pybox|'Reference:Year'|
    \item \pybox|'Reference:Pages'|
    \item \pybox|'Apparatus:Kind'|
\end{itemize*}

% This weirdness is necessary to prevent the list from running over the margin
\noindent\begin{itemize*}
    \item \pybox|'Apparatus:Facility'|
    \item \pybox|'Apparatus:Institution'|
\end{itemize*}

Only the first author is printed when \pybox|Reference| or
\pybox|Reference:Authors| is selected because the whole author list may be
quite long.

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for automated testing, and currently has
100\% line and branch coverage for all of the executable code in the repository. This
means that the tests execute every line of code at least once, and evaluate
every branch statement (e.g., if-then-else statements) to execute every condition
at least once.

Travis-CI\footnote{\url{https://travis-ci.org/pr-omethe-us/PyKED}} provides continuous
integration service, including running the test suite, building and distributing binary
installer packages, and building and publishing the online documentation. This automation
runs the test suite after every change to the source code, keeps the documentation
up-to-date with the latest changes, and streamlines the release of new versions.

>>>>

We therefore believe there remains a need for an open, community-focused and
developed, combustion\slash chemical kinetics data format. In this work, we
present a new, open-source, human- and machine-readable data standard for
fundamental combustion experiments, \ck{}, and offer tools for easily working
with data encoded in this format. Niemeyer recently introduced an initial
version of the \ck{} format~\autocite{Niemeyer:2016wf}, and in this work we
further formalize and develop the standard. We also discuss a related Python
software tool for validating and working with \ck{} files: \pk{}. Our
motivations are similar those of the PrIMe and ReSpecTh teams: the \ck{} project
will enable easy sharing and use of fundamental combustion data, for the
(primary) purposes of developing and validating predictive chemical kinetic
models. However, we make usability a major design focus, and plan to share all
data and software openly to cultivate a community of user-contributors.

@@

This section provides a brief introduction to the current version of the
\ck{} database format, v0.1.6, which represents a functional standard
for documenting autoignition measurements in shock tubes and rapid compression machines.
Here we do not include a complete listing of available fields; a complete reference for the
schema can be found in the online
documentation.\footnote{\url{https://pr-omethe-us.github.io/PyKED/schema-docs.html}}
In Section~\ref{sec:usage-example}, we provide examples of \ck{} files and
representative use cases. We indicate \yabox|yaml| keywords or values using text with
gray background, and \pybox|Python| code using text with a yellow background.

\ck{} files use the YAML data serialization format~\autocite{yaml:1.2}. This
format offers the advantages of being human readable, written in plain text, and
having parsers in most common programming languages, including Python, C++, Java,
Perl, MATLAB, and many others. The YAML syntax is quite simple: the basic file
structure consists of mappings, delimited by a colon. The key for the mapping is
on the left of the colon, and the value on the right can be a single value,
a sequence of values, a nested mapping, or some combination of these:
%
\begin{yamlbox}
key1: value  # Single-value mapping
key2:  # Sequence format
  - value
  - value
key3:  # Nested mapping
  key4: 0
key5:  # Sequence of mappings
  - key-s1: 0
    key-s2: value
  - key-s2: value
    key-s1: 0
\end{yamlbox}

The \yabox|value| can be a string, integer, or floating-point number. We designed
the \ck{} format to include all information necessary to simulate a
given experiment. A \ck{} file is generally broken into two main sections.
The first section details all the ``meta'' information about the experiment
and the \ck{} file itself. This section uses the common \yabox|author| mapping
for any fields that specify an author. The \yabox|author| mapping
contains the following fields:
%
\begin{itemize}
    \item \yabox|name| (required, string): The author's full name
    \item \yabox|ORCID| (optional, string): the author's unique ORCID code
\end{itemize}
%
More generally for the meta information, the required keys in this section
are:
%
\begin{itemize}
    \item \yabox|file-author| (required, \yabox|author|-type mapping): The
    author of the \ck{} file
    \item \yabox|file-version| (required, integer): The version of the \ck{}
    file
    \item \yabox|chemked-version| (required, string): The version of the \ck{}
    schema to which this file conforms
    \item \yabox|reference| (required, mapping): The reference information for
    the published article associated with the data in the file. The fields in this
    mapping are:
    \begin{itemize}
        \item \yabox|authors| (required, sequence): A sequence of \yabox|author|
        mappings
        \item \yabox|journal| (required, string): The name of the publishing
        journal
        \item \yabox|year| (required, integer): The year of publication
        \item \yabox|doi| (optional, string): The article DOI
        \item \yabox|volume| (required, integer): The journal volume number
        \item \yabox|pages| (optional, string): The article pages
        \item \yabox|detail| (optional, string): A description of from where the
        data originated (e.g., figure or table number)
    \end{itemize}
    \item \yabox|experiment-type| (required, string): Currently, only
    \yabox|ignition delay| is supported
    \item \yabox|apparatus| (required, string): The type of apparatus used to
    perform the experiment (\yabox|shock tube| or \yabox|rapid compression machine|)
\end{itemize}

The second section of the file encodes the experimental data. The \ck{} file
describes these using a sequence of mappings, with the following information required
in each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units
    \item \yabox|pressure| (required, string): The pressure of the experiment,
    with units
    \item \yabox|composition| (required, sequence): The composition of the
    mixture in the experiment, described via a sequence of mappings with the fields
    \begin{itemize}
        \item \yabox|species-name| (required, string): The name of the species
        \item \yabox|mole-fraction|, \yabox|mole-percent|, \yabox|mass-fraction|
        (required, float): The mole fraction or percent, or the mass fraction.
        Only one of the three is permitted in a given \yabox|composition|
        sequence.
        \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
        \yabox|elemental-composition| (required, string or sequence): The InChI
        or SMILES representing the molecule, or its atomic or elemental
        composition (\yabox|atomic-composition| and
        \yabox|elemental-composition| are synonyms) as a sequence
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), or \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

The top-level key for the sequence is called \yabox|datapoints|. Each of the
quantities in an element must be specified with units. This should be done as a
single string associated with the first element of the sequence. The units of
the quantity are validated to ensure appropriate dimensionality
for the quantity. In addition, each of the quantities in an element can
optionally be assigned an uncertainty. This uncertainty can be either absolute
or relative, and is specified as an element of the sequence of the associated key.
For example, the absolute uncertainty of the temperature and the relative
uncertainty of the ignition delay might be specified as:
%
\begin{yamlbox}
datapoints:
  - temperature:
      - 1100 kelvin
      - uncertainty-type: absolute
        uncertainty: 10 kelvin
    ignition-delay:
      - 10 us
      - uncertainty-type: relative
        uncertainty: 0.1
    ...
\end{yamlbox}

We have begun building an open repository of \ck{} files, available online at
GitHub.\footnote{\url{https://github.com/pr-omethe-us/ChemKED-database}}
We welcome submissions from the community; these can be made via the standard pull request
on GitHub. The authors also encourage questions and problems to be submitted either via
email or as issues on GitHub. In particular, researchers interested in converters for
internal data formats to the \ck{} format are encouraged to reach out;
the \pk{} package (described in more detail in Sec.~\ref{sec:pyked-architecture})
currently provides converters to and from the ReSpecTh format~\autocite{Varga2015b}.
While we plan to continue growing this database---and hope for submissions from
the community---others can freely download files, or in fact copy (``fork,'' in GitHub
parlance) the entire database for their own purposes.

%====================================================================
\section{PyKED architecture}\label{sec:pyked-architecture}
%
\pk{} is a Python package that provides the reference implementation
of the interface to \ck{} files~\autocite{PyKED}. \pk{} reads \ck{} files, validates
their structure and content, and allows the user to interact with the data contained
in the \ck{} file.

\pk{} provides the basic user interface to a \ck{} file through the
\pybox|ChemKED| class. The \pybox|ChemKED| class constructor takes the name
of a \ck{} file or a Python dictionary containing the contents of a \ck{} file
as its argument. When the file or dictionary is loaded, \pk{} validates its
format and contents using the Python package Cerberus \autocite{cerberus}. The
schema used for validation of the \ck{} files is available publicly in the
\texttt{schemas} directory of the PyKED source code
repository.\footnote{\url{https://github.com/pr-omethe-us/PyKED/tree/master/pyked/schemas}}
The schema comprises multiple YAML files to ease its extension to describe other
experimental measurements.

@@

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class,
the \pybox|DataPoint| stores information as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only---no validation is done of the
    value.
    \item \pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|,
    \pybox|pressure_rise|: The value of these data are stored as instances of
    the \pybox|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole-percent|,
    \yabox|mole-fraction|, or \yabox|mass-fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole-percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole-percent'|,
    \pybox|'mole-fraction'|, or \pybox|'mass-fraction'|
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
    \item \pybox|compression_time|: If the \ck{} file encodes an RCM experiment,
    the length of the compression stroke may be included
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
\end{itemize}

The \pybox|DataPoint| class defines two instance methods:
\pybox|get_cantera_mole_fraction()| and \pybox|get_cantera_mass_fraction()|.
These methods output the composition of the reactant mixture to a
format that can be used to set the composition of a
Cantera~\pybox|Solution|~\autocite{Cantera:2.3.0}.
The \pybox|composition| specification does not contain the molecular
weights of the components, so conversion between mole fractions and mass
fractions is not currently possible. (Future versions of \pk{} may support this
feature via, e.g., online lookup of species using their InChI\slash SMILES
identifiers.)

The \pybox|ChemKED| class defines three instance methods:
\pybox|get_dataframe()|, \pybox|write_file()|, and \pybox|convert_to_ReSpecTh()|.
The \pybox|get_dataframe()| method provides an instance of a
Pandas \pybox|DataFrame|~\autocite{pandas} that contains the information in the
list of \pybox|DataPoint|s. The user can specify the columns included in the
\pybox|DataFrame| by passing a list of column names to the
\pybox|output_columns| argument of the \pybox|get_dataframe()| method. The
possible columns are not case-sensitive and are:
%
\noindent\begin{itemize*}
    \item \pybox|'Temperature'|
    \item \pybox|'Pressure'|
    \item \pybox|'Ignition Delay'|
    \item \pybox|'Composition'|
    \item \pybox|'Equivalence Ratio'|
    \item \pybox|'Reference'|
    \item \pybox|'Apparatus'|
    \item \pybox|'Experiment Type'|
    \item \pybox|'File Author'|
    \item \pybox|'File Version'|
    \item \pybox|'ChemKED Version'|
\end{itemize*}

In addition, specific fields from the \pybox|Reference| and \pybox|Apparatus|
attributes can be included by specifying the name after a colon. These options
are:
%
\noindent\begin{itemize*}
    \item \pybox|'Reference:Volume'|
    \item \pybox|'Reference:Journal'|
    \item \pybox|'Reference:DOI'|
    \item \pybox|'Reference:Authors'|
    \item \pybox|'Reference:Detail'|
    \item \pybox|'Reference:Year'|
    \item \pybox|'Reference:Pages'|
    \item \pybox|'Apparatus:Kind'|
    \item \pybox|'Apparatus:Facility'|
\end{itemize*}

% This weirdness is necessary to prevent the list from running over the margin
\noindent\begin{itemize*}
    \item \pybox|'Apparatus:Institution'|
\end{itemize*}

Only the first author is printed when \pybox|Reference| or
\pybox|Reference:Authors| is selected because the whole author list may be
quite long. The \pybox|write_file()| method writes another \ck{} YAML file based on
the internal attributes, while \pybox|convert_to_ReSpecTh()| converts the \ck{}
to a ReSpecTh XML file. In the latter case, some information may be lost, as \ck{}
files both encode more details and specify more granularity of some information than
ReSpecTh files.

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for automated testing, and currently has
100\% line and branch coverage for all executable code in the repository. This
means that the tests execute every line of code at least once, and evaluate
every branch statement (e.g., if-then-else statements) to execute every condition
at least once.
Travis-CI\footnote{\url{https://travis-ci.org/pr-omethe-us/PyKED}} provides continuous
integration service, including running the test suite, building and distributing binary
installer packages, and building and publishing the online documentation. This automation
runs the test suite after every change to the source code, keeps the documentation
up-to-date with the latest changes, and streamlines the release of new versions.
